### 2016-03-24 docs/online_supporting_information.tex
fixes fig s3 legend typo

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/formatted_figures/formatted_figureS4.png}
  \caption{Community-wide synchrony of species percent cover from model simulation experiments for the Idaho community with \textit{Artemisia tripartita} removed. Synchrony of species' percent cover for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Error bars represent the upper and lower 95\% quantiles from model simulations.}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/formatted_figures/formatted_figureS4.png}
  \caption{Community-wide synchrony of species' per capita growth rates from model simulation experiments for the Idaho community with \textit{Artemisia tripartita} removed. Synchrony of species' percent cover for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Error bars represent the upper and lower 95\% quantiles from model simulations.}
\end{figure}
